---
title: "HW1"
author: "Andrew Li"
date: "2022-09-24"
output: github_document
---

```{r setup, include=FALSE}
library(dplyr)
library(nycflights13)
library(ggplot2)
```

1. How many flights have a missing dep_time? What other variables are missing?
What might these rows represent?
```{r}
flights %>%
  filter(is.na(dep_time))
```
Here we can see that 8,255 flights are missing a `dep_time` value. Other missing
variables include `dep_delay`, `arr_time`, `arr_delay`, and `air_time`. These rows
may represent any flights that were canceled.



2. Currently `dep_time` and `sched_dep_time` are convenient to look at, but
hard to compute with because they’re not really continuous numbers. Convert
them to a more convenient representation of number of minutes since midnight.
```{r}
flights %>%
  mutate(dep_time = ((dep_time %/% 100) * 60) + dep_time %% 100,
         sched_dep_time = ((sched_dep_time %/% 100) * 60) + sched_dep_time %% 100)
```



3. Look at the number of canceled flights per day. Is there a pattern? Is the
proportion of canceled flights related to the average delay? Use multiple
`dyplr` operations, all on one line, concluding with
`ggplot(aes(x= ,y=)) + geom_point()`
```{r}
flights %>%
  group_by(day) %>%
  summarise(average_delay = mean(dep_delay, na.rm=T),
            total_flights = n(),
            canceled_flights = sum(is.na(dep_delay)),
            proportion_canceled = canceled_flights / total_flights) %>%
  ggplot(aes(x = average_delay, y = proportion_canceled)) + geom_point()
```

There seems to be a positive correlation between the `average_delay` and
`proportion_cancelled`. That is, the larger the departure delay, the more likely
it is that the flight is cancelled altogether.
